Fourmile Calibrations and Output

### 2025-01-17 fourmile_output_dec2024.Rmd
found out what was wrong with grid_all KGE: 9/12/13 Q still included (not in cal but copied from elsewhere when putting together discharge_all.csv)
updated most recent cals (still need grid 2014-2020) and forward runs

```{r look at kge, echo = F}

# kge_plot <- ggplot(kge, aes(year_missing, KGE, shape = input_data, color = input_data)) + geom_point(size = 3) +
#   theme_bw()
# 
# ggplotly(kge_plot)

@@

# grid_2011 <- read_cals(grid_2011., name = 'grid_2011')
# grid_2012 <- read_cals(grid_2012., name = 'grid_2012')
# grid_2013 <- read_cals(grid_2013., name = 'grid_2013')
# grid_2014 <- read_cals(grid_2014., name = 'grid_2014')
# grid_2015 <- read_cals(grid_2015., name = 'grid_2015')
# grid_2016 <- read_cals(grid_2016., name = 'grid_2016')
# grid_2017 <- read_cals(grid_2017., name = 'grid_2017')
# grid_2018 <- read_cals(grid_2018., name = 'grid_2018')
# grid_2019 <- read_cals(grid_2019., name = 'grid_2019')
# grid_2020 <- read_cals(grid_2020., name = 'grid_2020')
grid_all <- read_cals(grid_all.c, name = 'grid_all')

# grid <- bind_rows(grid_2011, grid_2012, grid_2013, grid_2014, grid_2015,
#                   grid_2016, grid_2017, grid_2018, grid_2019, grid_2020,
#                   grid_all) %>%
#   mutate(input_data = 'grid') %>%
#   mutate(year_missing_almost = gsub('grid_', '', cal)) %>%
#   mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
#   dplyr::select(-c(year_missing_almost)) %>%
#   rename(param = Parameter) %>%
#   filter(!param == 'locGrw',
#          !param == 'tempRes')

grid <- grid_all %>%
  mutate(input_data = 'grid') %>%
  mutate(year_missing_almost = gsub('grid_', '', cal)) %>%
  mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
  dplyr::select(-c(year_missing_almost)) %>%
  rename(param = Parameter) %>%
  filter(!param == 'locGrw',
         !param == 'tempRes')

# statn_2011 <- read_cals(statn_2011, name = 'statn_2011')
# statn_2012 <- read_cals(statn_2012, name = 'statn_2012')
# statn_2013 <- read_cals(statn_2013, name = 'statn_2013')
# statn_2014 <- read_cals(statn_2014, name = 'statn_2014')
# statn_2015 <- read_cals(statn_2015, name = 'statn_2015')
# statn_2016 <- read_cals(statn_2016, name = 'statn_2016')
# statn_2017 <- read_cals(statn_2017, name = 'statn_2017')
# statn_2018 <- read_cals(statn_2018, name = 'statn_2018')
# statn_2019 <- read_cals(statn_2019, name = 'statn_2019')
# statn_2020 <- read_cals(statn_2020, name = 'statn_2020')
statn_all <- read_cals(statn_all., name = 'statn_all')

# statn <- bind_rows(statn_2011, statn_2012, statn_2013, statn_2014, statn_2015,
#                   statn_2016, statn_2017, statn_2018, statn_2019, statn_2020,
#                   statn_all) %>%
#   mutate(input_data = 'statn') %>%
#   mutate(year_missing_almost = gsub('statn_', '', cal)) %>%
#   mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
#   dplyr::select(-c(year_missing_almost)) %>%
#   rename(param = Parameter) %>%
#   filter(!param == 'locGrw',
#          !param == 'tempRes')

statn <- statn_all %>%
  mutate(input_data = 'statn') %>%
  mutate(year_missing_almost = gsub('statn_', '', cal)) %>%
  mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
  dplyr::select(-c(year_missing_almost)) %>%
  rename(param = Parameter) %>%
  filter(!param == 'locGrw',
         !param == 'tempRes')

@@

# mean_params <- params %>%
#   group_by(param, input_data) %>%
#   summarize(mean = mean(value))
# 
# plotdens_params <- function(param_name) {
#   params %>%
#     filter(param == param_name) %>%
#     ggplot(aes(x = value,
#                fill = input_data, 
#                color = input_data)) + 
#     geom_density(alpha=0.5) +
#     geom_vline(data=filter(mean_params, param == param_name), 
#                aes(xintercept=mean, color=input_data),
#              linetype="dashed", linewidth=0.75) +
#     ggtitle(param_name) +
#     theme_bw()
# }
# 
# name <- levels(params$param)
# 
# lapply(name, plotdens_params)

@@

# rm(statn_2011, statn_2012, statn_2013, statn_2014, statn_2015,
#                   statn_2016, statn_2017, statn_2018, statn_2019, statn_2020,
#                   statn_all., statn_all)

rm(statn_all)

@@

# grid_2011_burn <- read_cals_burn(grid_2011., name = 'grid_2011')
# grid_2012_burn <- read_cals_burn(grid_2012., name = 'grid_2012')
# grid_2013_burn <- read_cals_burn(grid_2013., name = 'grid_2013')
# grid_2014_burn <- read_cals_burn(grid_2014., name = 'grid_2014')
# grid_2015_burn <- read_cals_burn(grid_2015., name = 'grid_2015')
# grid_2016_burn <- read_cals_burn(grid_2016., name = 'grid_2016')
# grid_2017_burn <- read_cals_burn(grid_2017., name = 'grid_2017')
# grid_2018_burn <- read_cals_burn(grid_2018., name = 'grid_2018')
# grid_2019_burn <- read_cals_burn(grid_2019., name = 'grid_2019')
# grid_2020_burn <- read_cals_burn(grid_2020., name = 'grid_2020')
grid_all_burn <- read_cals_burn(grid_all.c, name = 'grid_all')

# grid_burn <- bind_rows(grid_2011_burn, 
#                   grid_2012_burn, 
#                   grid_2013_burn, 
#                   grid_2014_burn, 
#                   grid_2015_burn,
#                   grid_2016_burn, 
#                   grid_2017_burn, 
#                   grid_2018_burn, 
#                   grid_2019_burn, 
#                   grid_2020_burn,
#                   grid_all_burn) %>%
#   mutate(input_data = 'grid') %>%
#   mutate(year_missing_almost = gsub('grid_', '', cal)) %>%
#   mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
#   dplyr::select(-c(year_missing_almost))

grid_burn <- grid_all_burn %>%
  mutate(input_data = 'grid') %>%
  mutate(year_missing_almost = gsub('grid_', '', cal)) %>%
  mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
  dplyr::select(-c(year_missing_almost))

# now do statn burn params
# statn_2011_burn <- read_cals_burn(statn_2011, name = 'statn_2011')
# statn_2012_burn <- read_cals_burn(statn_2012, name = 'statn_2012')
# statn_2013_burn <- read_cals_burn(statn_2013, name = 'statn_2013')
# statn_2014_burn <- read_cals_burn(statn_2014, name = 'statn_2014')
# statn_2015_burn <- read_cals_burn(statn_2015, name = 'statn_2015')
# statn_2016_burn <- read_cals_burn(statn_2016, name = 'statn_2016')
# statn_2017_burn <- read_cals_burn(statn_2017, name = 'statn_2017')
# statn_2018_burn <- read_cals_burn(statn_2018, name = 'statn_2018')
# statn_2019_burn <- read_cals_burn(statn_2019, name = 'statn_2019')
# statn_2020_burn <- read_cals_burn(statn_2020, name = 'statn_2020')
statn_all_burn <- read_cals_burn(statn_all., name = 'statn_all')

# statn_burn <- bind_rows(statn_2011_burn, 
#                   statn_2012_burn, 
#                   statn_2013_burn, 
#                   statn_2014_burn, 
#                   statn_2015_burn,
#                   statn_2016_burn, 
#                   statn_2017_burn, 
#                   statn_2018_burn, 
#                   statn_2019_burn, 
#                   statn_2020_burn,
#                   statn_all_burn) %>%
#   mutate(input_data = 'statn') %>%
#   mutate(year_missing_almost = gsub('statn_', '', cal)) %>%
#   mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
#   dplyr::select(-c(year_missing_almost))

statn_burn <- statn_all_burn %>%
  mutate(input_data = 'statn') %>%
  mutate(year_missing_almost = gsub('statn_', '', cal)) %>%
  mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
  dplyr::select(-c(year_missing_almost))

@@

```{r echo = FALSE, message = FALSE, warning = FALSE}
params2 <- params %>%
  mutate(burn = 'no') %>%
  filter(param %in% c('a_rain',
                        'a_snow',
                        'soilMaxInfSummer',
                        'soilMaxDPS',
                        'lagSurfaceRunoff',
                        'soilDistMPSLPS'))

@@

# Outlet results

## Hydrograph

```{r hydrographs, echo = FALSE, message = FALSE, warning = FALSE, fig.width=10, fig.height=6}

flow <- read_csv('discharge_all.csv') %>%
  replace(.==-9999, NA) %>%
  rename(date = time) %>%
  mutate(date = mdy(date))

flow_pivot <- flow %>%
  pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>%
  mutate(year = as.factor(year(date)))

q <- ggplot(flow_pivot, aes(date, q_m3s, color = cal_run)) +
  geom_line() +
  scale_color_manual(name="cal_run", values=c('obs' = 'black',
                                            # "grid_2011"="seagreen",
                                            # "grid_2012"="seagreen2",
                                            # "grid_2013"="steelblue",
                                            # "grid_2014"='dodgerblue',
                                            # "grid_2015" = "cyan3",
                                            # 'grid_2016' = 'blue',
                                            # 'grid_2017' = 'blue4',
                                            # 'grid_2018' = 'cadetblue',
                                            # 'grid_2019' = 'lightgreen',
                                            # 'grid_2020' = 'olivedrab',
                                            'grid_all' = 'steelblue3',
                                            # "statn_2011"="maroon",
                                            # "statn_2012"="deeppink4",
                                            # "statn_2013"="deeppink",
                                            # "statn_2014"='purple',
                                            # "statn_2015" = "mediumorchid1",
                                            # 'statn_2016' = 'indianred',
                                            # 'statn_2017' = 'sienna',
                                            # 'statn_2018' = 'salmon2',
                                            # 'statn_2019' = 'mediumpurple1',
                                            # 'statn_2020' = 'violetred',
                                            'statn_all' = 'red')) +
  theme_bw(base_size=20)

ggplotly(q)

## Cumulative volume

```{r cumq, echo = FALSE, message = FALSE, warning = FALSE}

flow_cumq <- flow_pivot %>%
  mutate(month = month(date)) %>%
  filter(month %in% c(4:9)) %>%
  dplyr::select(-month) %>%
  #pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>%
  mutate(vol_m3 = q_m3s * 86400) %>%
  group_by(cal_run, year(date)) %>%
  mutate(cumsum = cumsum(replace_na(vol_m3, 0))) %>%
  #rename(year = 4) %>%
  mutate(year = as.factor(year)) %>%
  ungroup()

#plot annual cumulative Q vals for ensembles
plot_cumulq_yr_ <- function(calyear) {
  {flow_cumq %>%
    filter(year == calyear) %>%
    ggplot(aes(x = date,
               y = cumsum,
               color = cal_run)) +
    geom_line() +
scale_color_manual(name="cal_run", values=c('obs' = 'black',
                                            # "grid_2011"="seagreen",
                                            # "grid_2012"="seagreen2",
                                            # "grid_2013"="steelblue",
                                            # "grid_2014"='dodgerblue',
                                            # "grid_2015" = "cyan3",
                                            # 'grid_2016' = 'blue',
                                            # 'grid_2017' = 'blue4',
                                            # 'grid_2018' = 'cadetblue',
                                            # 'grid_2019' = 'lightgreen',
                                            # 'grid_2020' = 'olivedrab',
                                            'grid_all' = 'steelblue3',
                                            # "statn_2011"="maroon",
                                            # "statn_2012"="deeppink4",
                                            # "statn_2013"="deeppink",
                                            # "statn_2014"='purple',
                                            # "statn_2015" = "mediumorchid1",
                                            # 'statn_2016' = 'indianred',
                                            # 'statn_2017' = 'sienna',
                                            # 'statn_2018' = 'salmon2',
                                            # 'statn_2019' = 'mediumpurple1',
                                            # 'statn_2020' = 'violetred',
                                            'statn_all' = 'red')) +
    ggtitle(calyear) +
    theme_bw() +
    labs(y = 'Volume (m^3)')} %>%
    ggplotly()
}

name <- levels(flow_cumq$year)

cumulative_plots <- lapply(name, plot_cumulq_yr_)

htmltools::tagList(cumulative_plots)

cumulative_plots

## KGE

### Overall KGE

```{r kge overall, echo = FALSE, message = FALSE, warning = FALSE}

# flow_kge_all <- flow %>%
#   summarize(grid2011 = KGE(grid_2011, obs),
#             grid2012 = KGE(grid_2012, obs),
#             grid2013 = KGE(grid_2013, obs),
#             grid2014 = KGE(grid_2014, obs),
#             grid2015 = KGE(grid_2015, obs),
#             grid2016 = KGE(grid_2016, obs),
#             grid2017 = KGE(grid_2017, obs),
#             grid2018 = KGE(grid_2018, obs),
#             grid2019 = KGE(grid_2019, obs),
#             grid2020 = KGE(grid_2020, obs),
#             gridall = KGE(grid_all, obs),
#             statn2011 = KGE(statn_2011, obs),
#             statn2012 = KGE(statn_2012, obs),
#             statn2013 = KGE(statn_2013, obs),
#             statn2014 = KGE(statn_2014, obs),
#             statn2015 = KGE(statn_2015, obs),
#             statn2016 = KGE(statn_2016, obs),
#             statn2017 = KGE(statn_2017, obs),
#             statn2018 = KGE(statn_2018, obs),
#             statn2019 = KGE(statn_2019, obs),
#             statn2020 = KGE(statn_2020, obs),
#             statnall = KGE(statn_all, obs)) %>%
#     mutate_if(is.numeric,
#             round,
#             digits = 2)

flow_kge_all <- flow %>%
  summarize(
            gridall = KGE(grid_all,
                          obs, 
                          na.rm=T, 
                          method='2012'),
            statnall = KGE(statn_all, 
                           obs, 
                           na.rm=T,
                           method='2012')) %>%
    mutate_if(is.numeric,
            round,
            digits = 2)

flow_kge_all <- flow_kge_all %>%
  pivot_longer(everything()) %>%
  arrange(value)

kable(flow_kge_all) %>%
  kable_styling(full_width = F)

### KGE by year

```{r kge by year, echo = FALSE, message = FALSE, warning = FALSE}

flow_year <- flow %>%
  mutate(year = year(date)) %>%
  group_by(year) %>%
  summarize(
    # grid2011 = KGE(grid_2011, obs),
    #         grid2012 = KGE(grid_2012, obs),
    #         grid2013 = KGE(grid_2013, obs),
    #         grid2014 = KGE(grid_2014, obs),
    #         grid2015 = KGE(grid_2015, obs),
    #         grid2016 = KGE(grid_2016, obs),
    #         grid2017 = KGE(grid_2017, obs),
    #         grid2018 = KGE(grid_2018, obs),
    #         grid2019 = KGE(grid_2019, obs),
    #         grid2020 = KGE(grid_2020, obs),
            gridall = KGE(grid_all, obs, na.rm = T, method='2012'),
            # statn2011 = KGE(statn_2011, obs),
            # statn2012 = KGE(statn_2012, obs),
            # statn2013 = KGE(statn_2013, obs),
            # statn2014 = KGE(statn_2014, obs),
            # statn2015 = KGE(statn_2015, obs),
            # statn2016 = KGE(statn_2016, obs),
            # statn2017 = KGE(statn_2017, obs),
            # statn2018 = KGE(statn_2018, obs),
            # statn2019 = KGE(statn_2019, obs),
            # statn2020 = KGE(statn_2020, obs),
            statnall = KGE(statn_all, obs, na.rm=T, method='2012')) %>%
    mutate_if(is.numeric,
            round,
            digits = 2)

flow_kge <- flow_year %>%
  pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>%
  pivot_wider(names_from = 'year', values_from = 'kge')

flow_kge %>%
  kable(.) %>%
  kable_styling()

flow_plot <- flow_year %>%
  pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>%
  mutate(year = as.factor(year))

# add all to the plot below
kge_all <- flow_kge_all %>%
  mutate(year = 'all years') %>%
  rename(model_run = name,
         kge = value)

flow_plot_updated <- bind_rows(flow_plot, kge_all)

ggplot(flow_plot_updated, aes(x = model_run, y = year, fill = kge)) +
  geom_tile(color = "white") +
  scale_fill_viridis_c(option = "viridis", name = "KGE", direction = -1) +
  geom_text(aes(label = round(kge, 2)), color = "grey", size = 2.5) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(y = "Year")

<!-- ### Annual KGE plots -->

<!-- ```{r wy plots, echo = FALSE, message = FALSE, warning = FALSE} -->

<!-- plot_kge <- function(calyear) { -->
<!--   flow_plot %>% -->
<!--     filter(year == calyear) %>% -->
<!--     ggplot(aes(x = model_run, -->
<!--                y = kge)) + -->
<!--     geom_point(size=3) + -->
<!--     ggtitle(calyear) + -->
<!--     theme_bw() + -->
<!--     theme(axis.text.x = element_text(angle = 45, hjust=1)) -->
<!-- } -->

<!-- name <- levels(flow_plot$year) -->

<!-- lapply(name, plot_kge) -->

@@

## Pbias

### Overall pbias

```{r pbias overall, echo = FALSE, message = FALSE, warning = FALSE}

flow_pbias_all <- flow %>%
  summarize(
    # grid2011 = pbias(grid_2011, obs),
    #         grid2012 = pbias(grid_2012, obs),
    #         grid2013 = pbias(grid_2013, obs),
    #         grid2014 = pbias(grid_2014, obs),
    #         grid2015 = pbias(grid_2015, obs),
    #         grid2016 = pbias(grid_2016, obs),
    #         grid2017 = pbias(grid_2017, obs),
    #         grid2018 = pbias(grid_2018, obs),
    #         grid2019 = pbias(grid_2019, obs),
    #         grid2020 = pbias(grid_2020, obs),
            gridall = pbias(grid_all, obs),
            # statn2011 = pbias(statn_2011, obs),
            # statn2012 = pbias(statn_2012, obs),
            # statn2013 = pbias(statn_2013, obs),
            # statn2014 = pbias(statn_2014, obs),
            # statn2015 = pbias(statn_2015, obs),
            # statn2016 = pbias(statn_2016, obs),
            # statn2017 = pbias(statn_2017, obs),
            # statn2018 = pbias(statn_2018, obs),
            # statn2019 = pbias(statn_2019, obs),
            # statn2020 = pbias(statn_2020, obs),
            statnall = pbias(statn_all, obs)) %>%
    mutate_if(is.numeric,
            round,
            digits = 2)

flow_pbias_all <- flow_pbias_all %>%
  pivot_longer(everything()) %>%
  arrange(abs(value))

kable(flow_pbias_all) %>%
  kable_styling(full_width = F)

### Pbias by year

```{r pbias by year, echo = FALSE, message = FALSE, warning = FALSE}

flow_year <- flow %>%
  mutate(year = year(date)) %>%
  group_by(year) %>%
  summarize(
    # grid2011 = pbias(grid_2011, obs),
    #         grid2012 = pbias(grid_2012, obs),
    #         grid2013 = pbias(grid_2013, obs),
    #         grid2014 = pbias(grid_2014, obs),
    #         grid2015 = pbias(grid_2015, obs),
    #         grid2016 = pbias(grid_2016, obs),
    #         grid2017 = pbias(grid_2017, obs),
    #         grid2018 = pbias(grid_2018, obs),
    #         grid2019 = pbias(grid_2019, obs),
    #         grid2020 = pbias(grid_2020, obs),
            gridall = pbias(grid_all, obs),
            # statn2011 = pbias(statn_2011, obs),
            # statn2012 = pbias(statn_2012, obs),
            # statn2013 = pbias(statn_2013, obs),
            # statn2014 = pbias(statn_2014, obs),
            # statn2015 = pbias(statn_2015, obs),
            # statn2016 = pbias(statn_2016, obs),
            # statn2017 = pbias(statn_2017, obs),
            # statn2018 = pbias(statn_2018, obs),
            # statn2019 = pbias(statn_2019, obs),
            # statn2020 = pbias(statn_2020, obs),
            statnall = pbias(statn_all, obs)) %>%
    mutate_if(is.numeric,
            round,
            digits = 2)

flow_pbias <- flow_year %>%
  pivot_longer(!year, names_to = 'model_run', values_to = 'pbias') %>%
  pivot_wider(names_from = 'year', values_from = 'pbias')

flow_pbias %>%
  kable(.) %>%
  kable_styling()

flow_plot <- flow_year %>%
  pivot_longer(!year, names_to = 'model_run', values_to = 'pbias') %>%
  mutate(year = as.factor(year))

# add all to the plot below
pbias_all <- flow_pbias_all %>%
  mutate(year = 'all years') %>%
  rename(model_run = name,
         pbias = value)

flow_plot_updated <- bind_rows(flow_plot, pbias_all)

ggplot(flow_plot_updated, aes(x = model_run, y = year, fill = pbias)) +
  geom_tile(color = "white") +
   scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint = 0, name = "Pbias") +
  geom_text(aes(label = round(pbias, 2)), color = "black", size = 2.5) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(y = "Year")

<!-- ### Annual Pbias plots -->

<!-- ```{r pbias plots, echo = FALSE, message = FALSE, warning = FALSE} -->

<!-- plot_pbias <- function(calyear) { -->
<!--   flow_plot %>% -->
<!--     filter(year == calyear) %>% -->
<!--     ggplot(aes(x = model_run, -->
<!--                y = pbias)) + -->
<!--     geom_point(size=3) + -->
<!--     ggtitle(calyear) + -->
<!--     theme_bw() + -->
<!--     theme(axis.text.x = element_text(angle = 45, hjust=1)) -->
<!-- } -->

<!-- name <- levels(flow_plot$year) -->

<!-- lapply(name, plot_pbias) -->

@@

# RD and RG

- **Different units than streamflow (cms) and volume (m3)**
- **All in mm**

```{r rd and rg, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 14, fig.asp = 1, out.width = "100%"}

gw_gridall <- read_csv(here('38HRU_dec2024_updates/catchment_output/grid_all.csv'), skip = 3) %>%
  slice(-c(1,2)) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'grid_all') %>%
  mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))

>>>>

@@

grid_2011 <- read_cals(grid_2011., name = 'grid_2011')
grid_2012 <- read_cals(grid_2012., name = 'grid_2012')
grid_2013 <- read_cals(grid_2013., name = 'grid_2013')
# grid_2014 <- read_cals(grid_2014., name = 'grid_2014')
# grid_2015 <- read_cals(grid_2015., name = 'grid_2015')
# grid_2016 <- read_cals(grid_2016., name = 'grid_2016')
# grid_2017 <- read_cals(grid_2017., name = 'grid_2017')
# grid_2018 <- read_cals(grid_2018., name = 'grid_2018')
# grid_2019 <- read_cals(grid_2019., name = 'grid_2019')
# grid_2020 <- read_cals(grid_2020., name = 'grid_2020')
grid_all <- read_cals(grid_all.c, name = 'grid_all')

grid <- bind_rows(grid_2011, grid_2012, grid_2013, #grid_2014, grid_2015,
                  #grid_2016, grid_2017, grid_2018, grid_2019, grid_2020,
                  grid_all) %>%
  mutate(input_data = 'grid') %>%
  mutate(year_missing_almost = gsub('grid_', '', cal)) %>%
  mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
  dplyr::select(-c(year_missing_almost)) %>%
  rename(param = Parameter) %>%
  filter(!param == 'locGrw',
         !param == 'tempRes')

statn_2011 <- read_cals(statn_2011, name = 'statn_2011')
statn_2012 <- read_cals(statn_2012, name = 'statn_2012')
statn_2013 <- read_cals(statn_2013, name = 'statn_2013')
statn_2014 <- read_cals(statn_2014, name = 'statn_2014')
statn_2015 <- read_cals(statn_2015, name = 'statn_2015')
statn_2016 <- read_cals(statn_2016, name = 'statn_2016')
statn_2017 <- read_cals(statn_2017, name = 'statn_2017')
statn_2018 <- read_cals(statn_2018, name = 'statn_2018')
statn_2019 <- read_cals(statn_2019, name = 'statn_2019')
statn_2020 <- read_cals(statn_2020, name = 'statn_2020')
statn_all <- read_cals(statn_all., name = 'statn_all')

statn <- bind_rows(statn_2011, statn_2012, statn_2013, statn_2014, statn_2015,
                  statn_2016, statn_2017, statn_2018, statn_2019, statn_2020,
                  statn_all) %>%
  mutate(input_data = 'statn') %>%
  mutate(year_missing_almost = gsub('statn_', '', cal)) %>%
  mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
  dplyr::select(-c(year_missing_almost)) %>%
  rename(param = Parameter) %>%
  filter(!param == 'locGrw',
         !param == 'tempRes')

@@

mean_params <- params %>%
  group_by(param, input_data) %>%
  summarize(mean = mean(value))

plotdens_params <- function(param_name) {
  params %>%
    filter(param == param_name) %>%
    ggplot(aes(x = value,
               fill = input_data,
               color = input_data)) +
    geom_density(alpha=0.5) +
    geom_vline(data=filter(mean_params, param == param_name),
               aes(xintercept=mean, color=input_data),
             linetype="dashed", linewidth=0.75) +
    ggtitle(param_name) +
    theme_bw()
}

lapply(name, plotdens_params)

@@

rm(statn_2011, statn_2012, statn_2013, statn_2014, statn_2015,
                  statn_2016, statn_2017, statn_2018, statn_2019, statn_2020,
                  statn_all., statn_all)

@@

grid_2011_burn <- read_cals_burn(grid_2011., name = 'grid_2011')
grid_2012_burn <- read_cals_burn(grid_2012., name = 'grid_2012')
grid_2013_burn <- read_cals_burn(grid_2013., name = 'grid_2013')
# grid_2014_burn <- read_cals_burn(grid_2014., name = 'grid_2014')
# grid_2015_burn <- read_cals_burn(grid_2015., name = 'grid_2015')
# grid_2016_burn <- read_cals_burn(grid_2016., name = 'grid_2016')
# grid_2017_burn <- read_cals_burn(grid_2017., name = 'grid_2017')
# grid_2018_burn <- read_cals_burn(grid_2018., name = 'grid_2018')
# grid_2019_burn <- read_cals_burn(grid_2019., name = 'grid_2019')
# grid_2020_burn <- read_cals_burn(grid_2020., name = 'grid_2020')
grid_all_burn <- read_cals_burn(grid_all.c, name = 'grid_all')

grid_burn <- bind_rows(grid_2011_burn,
                  grid_2012_burn,
                  grid_2013_burn,
                  # grid_2014_burn,
                  # grid_2015_burn,
                  # grid_2016_burn,
                  # grid_2017_burn,
                  # grid_2018_burn,
                  # grid_2019_burn,
                  # grid_2020_burn,
                  grid_all_burn) %>%
  mutate(input_data = 'grid') %>%
  mutate(year_missing_almost = gsub('grid_', '', cal)) %>%
  mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
  dplyr::select(-c(year_missing_almost))

# now do statn burn params
statn_2011_burn <- read_cals_burn(statn_2011, name = 'statn_2011')
statn_2012_burn <- read_cals_burn(statn_2012, name = 'statn_2012')
statn_2013_burn <- read_cals_burn(statn_2013, name = 'statn_2013')
statn_2014_burn <- read_cals_burn(statn_2014, name = 'statn_2014')
statn_2015_burn <- read_cals_burn(statn_2015, name = 'statn_2015')
statn_2016_burn <- read_cals_burn(statn_2016, name = 'statn_2016')
statn_2017_burn <- read_cals_burn(statn_2017, name = 'statn_2017')
statn_2018_burn <- read_cals_burn(statn_2018, name = 'statn_2018')
statn_2019_burn <- read_cals_burn(statn_2019, name = 'statn_2019')
statn_2020_burn <- read_cals_burn(statn_2020, name = 'statn_2020')
statn_all_burn <- read_cals_burn(statn_all., name = 'statn_all')

statn_burn <- bind_rows(statn_2011_burn,
                  statn_2012_burn,
                  statn_2013_burn,
                  statn_2014_burn,
                  statn_2015_burn,
                  statn_2016_burn,
                  statn_2017_burn,
                  statn_2018_burn,
                  statn_2019_burn,
                  statn_2020_burn,
                  statn_all_burn) %>%
  mutate(input_data = 'statn') %>%
  mutate(year_missing_almost = gsub('statn_', '', cal)) %>%
  mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
  dplyr::select(-c(year_missing_almost))

@@

params2 <- params %>%
  mutate(burn = 'no') %>%
  filter(param %in% c('a_rain',
                        'a_snow',
                        'soilMaxInfSummer',
                        'soilMaxDPS',
                        'lagSurfaceRunoff',
                        'soilDistMPSLPS'))

@@

<!-- # Outlet results -->

<!-- ## Hydrograph -->

<!-- ```{r hydrographs, echo = FALSE, message = FALSE, warning = FALSE, fig.width=10, fig.height=6} -->

<!-- setwd('/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates') -->

<!-- flow <- read_csv('discharge_all.csv') %>% -->
<!--   replace(.==-9999, NA) %>% -->
<!--   rename(date = time) %>% -->
<!--   mutate(date = mdy(date))  -->

<!-- flow_pivot <- flow %>% -->
<!--   pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>% -->
<!--   mutate(year = as.factor(year(date))) -->

<!-- q <- ggplot(flow_pivot, aes(date, q_m3s, color = cal_run)) + -->
<!--   geom_line() + -->
<!--   scale_color_manual(name="cal_run", values=c('obs' = 'black', -->
<!--                                             # "grid_2011"="seagreen", -->
<!--                                             # "grid_2012"="seagreen2", -->
<!--                                             # "grid_2013"="steelblue", -->
<!--                                             # "grid_2014"='dodgerblue', -->
<!--                                             # "grid_2015" = "cyan3", -->
<!--                                             # 'grid_2016' = 'blue', -->
<!--                                             # 'grid_2017' = 'blue4', -->
<!--                                             # 'grid_2018' = 'cadetblue', -->
<!--                                             # 'grid_2019' = 'lightgreen', -->
<!--                                             # 'grid_2020' = 'olivedrab', -->
<!--                                             'grid_all' = 'steelblue3', -->
<!--                                             # "statn_2011"="maroon", -->
<!--                                             # "statn_2012"="deeppink4", -->
<!--                                             # "statn_2013"="deeppink", -->
<!--                                             # "statn_2014"='purple', -->
<!--                                             # "statn_2015" = "mediumorchid1", -->
<!--                                             # 'statn_2016' = 'indianred', -->
<!--                                             # 'statn_2017' = 'sienna', -->
<!--                                             # 'statn_2018' = 'salmon2', -->
<!--                                             # 'statn_2019' = 'mediumpurple1', -->
<!--                                             # 'statn_2020' = 'violetred', -->
<!--                                             'statn_all' = 'red')) + -->
<!--   theme_bw(base_size=20) -->

<!-- ggplotly(q) -->

@@

<!-- ## Cumulative volume -->

<!-- ```{r cumq, echo = FALSE, message = FALSE, warning = FALSE} -->

<!-- flow_cumq <- flow_pivot %>% -->
<!--   mutate(month = month(date)) %>% -->
<!--   filter(month %in% c(4:9)) %>% -->
<!--   dplyr::select(-month) %>% -->
<!--   #pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>% -->
<!--   mutate(vol_m3 = q_m3s * 86400) %>% -->
<!--   group_by(cal_run, year(date)) %>% -->
<!--   mutate(cumsum = cumsum(replace_na(vol_m3, 0))) %>% -->
<!--   #rename(year = 4) %>% -->
<!--   mutate(year = as.factor(year)) %>% -->
<!--   ungroup() -->

<!-- #plot annual cumulative Q vals for ensembles -->
<!-- plot_cumulq_yr_ <- function(calyear) { -->
<!--   {flow_cumq %>% -->
<!--     filter(year == calyear) %>% -->
<!--     ggplot(aes(x = date, -->
<!--                y = cumsum, -->
<!--                color = cal_run)) + -->
<!--     geom_line() + -->
<!-- scale_color_manual(name="cal_run", values=c('obs' = 'black', -->
<!--                                             # "grid_2011"="seagreen", -->
<!--                                             # "grid_2012"="seagreen2", -->
<!--                                             # "grid_2013"="steelblue", -->
<!--                                             # "grid_2014"='dodgerblue', -->
<!--                                             # "grid_2015" = "cyan3", -->
<!--                                             # 'grid_2016' = 'blue', -->
<!--                                             # 'grid_2017' = 'blue4', -->
<!--                                             # 'grid_2018' = 'cadetblue', -->
<!--                                             # 'grid_2019' = 'lightgreen', -->
<!--                                             # 'grid_2020' = 'olivedrab', -->
<!--                                             'grid_all' = 'steelblue3', -->
<!--                                             # "statn_2011"="maroon", -->
<!--                                             # "statn_2012"="deeppink4", -->
<!--                                             # "statn_2013"="deeppink", -->
<!--                                             # "statn_2014"='purple', -->
<!--                                             # "statn_2015" = "mediumorchid1", -->
<!--                                             # 'statn_2016' = 'indianred', -->
<!--                                             # 'statn_2017' = 'sienna', -->
<!--                                             # 'statn_2018' = 'salmon2', -->
<!--                                             # 'statn_2019' = 'mediumpurple1', -->
<!--                                             # 'statn_2020' = 'violetred', -->
<!--                                             'statn_all' = 'red')) + -->
<!--     ggtitle(calyear) + -->
<!--     theme_bw() + -->
<!--     labs(y = 'Volume (m^3)')} %>% -->
<!--     ggplotly() -->
<!-- } -->

<!-- name <- levels(flow_cumq$year) -->

<!-- cumulative_plots <- lapply(name, plot_cumulq_yr_) -->

<!-- htmltools::tagList(cumulative_plots) -->

<!-- cumulative_plots -->

@@

<!-- ## KGE -->

<!-- ### Overall KGE -->

<!-- ```{r kge overall, echo = FALSE, message = FALSE, warning = FALSE} -->
